Understanding domestic abuse

### 2019-07-30 case_for_support_TM_hacked.tex
Update case_for_support_TM_hacked.tex

>>>>

The University of Warwick has identified this as an important line of research, and has committed to supporting it, and the Centre for Operational Policing Research, into the future. As part of this commitment, Warwick Business School has allocated funding for a 4 year PhD studentship. This will begin during the grant period and then run on after the end date. This allows for continued impact related work, and provides capacity to build upon initial findings from this project.
